WDIAS : A Microservices-Based Weather Data Integration and Assimilation System\\

### 2020-05-06 Appendix/app_1_soa_and_actor_model.tex
Fix with Figure
Change all to \cref
Added fixes
Error Term,Correct Term,Description,No of Occurrences,Pages (absolute)
a.k.a.,aka.,,Shoudl be aka and need a comma,1,-1
[a-z] as well as,, as well as,Needs a comma before,3,-1
Also,Also,,Comma should be used at beginning of a sentence,1,-1
can not,cannot,Is a single word,4,-1
[fF]igure.\d,Figure n,There has to be a space like Figure 2.7,82,-1
Hence,Hence,,Comma should be used at beginning of a sentence,1,-1
in order to,to,Can be replaced with just to in many cases,4,-1
in to,into,Is a single word,1,-1
may be,maybe,Is a single word,2,-1
section,Se

In the initial phase of WDIAS architecture, it proposed with a \acrfull{soa} as shown in the \ref{fi:proposed_soa_arch_design}. Mainly it consist of 4 modules, namely:
- Import modules
Import modules are using for integration of data from different source which come in different data formats.
- Export modules
Export modules are using for data dissemination with different format which may required for different type of operations.
- Extension modules
Extension modules are capable of providing the data assimilation functionalities by providing some of key functionalities such as transformation, interpolation and validation. While data assimilation, existing timeseries may be modified or create new timeseries based on the system configurations.
- Adapter module
Adapter module is handling the complexity of integrating different data formats and storing them in the way that easy to search and retrieve.

>>>>

In the initial phase of WDIAS architecture, it proposed with a \acrfull{soa} as shown in the \cref{fi:proposed_soa_arch_design}. Mainly it consist of 4 modules, namely:
- Import modules
Import modules are using for integration of data from different source which come in different data formats.
- Export modules
Export modules are using for data dissemination with different format which may required for different type of operations.
- Extension modules
Extension modules are capable of providing the data assimilation functionalities by providing some of key functionalities such as transformation, interpolation and validation. While data assimilation, existing timeseries maybe modified or create new timeseries based on the system configurations.
- Adapter module
Adapter module is handling the complexity of integrating different data formats and storing them in the way that easy to search and retrieve.

### 2020-05-06 ThePaper.tex
Added fixes
Error Term,Correct Term,Description,No of Occurrences,Pages (absolute)
a.k.a.,aka.,,Shoudl be aka and need a comma,1,-1
[a-z] as well as,, as well as,Needs a comma before,3,-1
Also,Also,,Comma should be used at beginning of a sentence,1,-1
can not,cannot,Is a single word,4,-1
[fF]igure.\d,Figure n,There has to be a space like Figure 2.7,82,-1
Hence,Hence,,Comma should be used at beginning of a sentence,1,-1
in order to,to,Can be replaced with just to in many cases,4,-1
in to,into,Is a single word,1,-1
may be,maybe,Is a single word,2,-1
section,Section,S should be capital if used li

\dbc{Reduce background by ~25\%. Add a sentence on novetly on solution. Also. add a sentence on performance. Abstarct should not exceed 200 words.}
\gkc{Modified. 200 words.}

\begin{IEEEkeywords}
\db{Cloud computing, data assimilation, data integration, }microservice, weather
\end{IEEEkeywords}
\dbc{Update keyword list based on thesis. 4-5 keywords max}
\gkc{Thesis keywords are Cloud computing, data assimilation, data integration, hierarchical databases, microservice, weather. Do we need different set of keywords?}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
\label{pse:Introduction}
Weather prediction is essential to reduce the impacts caused by natural disasters and to effectively manage natural water resources. To enhance the accuracy of weather predictions, it requires to provide reliable and detailed weather data as inputs to \acrfull{nwm}s. Before feeding such diverse data collected from different sources, we need to convert data into NWMs compatible data format. Further we need to process data with lesser time to increase the lead time of forecasting, and need to handle bulk stream weather data.
Many third-party applications and researcher need to accessed processed weather data to make use of them. As few examples, logistics companies could use those data with their models to plan and schedule their deliveries. Agricultural insurance companies can warn the farmers, as well as calculate premiums based on anticipated weather patterns.
Even though there are many data integration systems, most systems are proprietary or closed source. For an island like Sri Lanka that having different kinds of weather seasons over the year than that software originated countries, those systems need to be highly customized. Thus it required to get support from the vendor to integrate and configure the system.
Most of the software existing out there are not up to date with the latest technology concepts such as Cloud Computing, and not using modern architecture pattern like microservice architecture that can use to build highly scalable and available systems, and use containerized applications to run systems independ of software platforms.

\db{Several forecasting systems are} developed with considering above factors for disaster management. Deltares developed the The \acrfull{fews}\cite{Werner2013TheSystem} in the Netherland for operational forecasting. It uses a model-centric approach, and implements the forecasting process as a combination of data modeling steps and data transformation algorithms. This framework does not have inherent hydrological modeling capabilities. But it capable of providing capability to create forecast workflows by integrate new models and algorithms. Also it uses a common data-model approach, and only allows models to interact with the system data via using one of the interfaces provided. All the timeseries data store in the common data model. This approach can consider as efficient for data store and access, but it has the inherent performance issues of access data in the database through a single data model. Interestingly, the \acrshort{fews} uses set of unique fields to identify timeseries one from another such as using timeseries's location and data type, as well as an id related to the source of the data. It provides an easy model integration with using the concept of the open modeling framework proposed by Open model integration \cite{Kokkonen2003InterfacingXML}. But the model adapter causes tide couple between models and the execution process of the \acrshort{fews}. This can cause issues when it required to do model unit testing and restrict the flexibility of running the models with parallel execution or external process execution.

\acrfull{lead} \cite{Droegemeier2005Service-OrientedWeather} uses the concept of dynamic workflow orchestration and data management in a Web services framework. To predict and analyze weather models by researchers, it requires many resources. Rather than each researcher runs and maintain own computer resources for the weather experiments, the \acrshort{lead} provides a pool of resources. The researchers use the resources pool to run their experiment in shorter amounts of time in higher scale. The \acrshort{lead} follows \acrfull{soa} with different service layers. Also it exposes services through a drag and drop interface to create new workflows. A workflow service in the \acrshort{lead} schedules and run built workflows with promising the maximum use of underline resource pool. \acrfull{dias} \cite{Kawasaki2018DataReduction} and \acrfull{madis} \cite{Macdermaid2005ArchitectureP2.39} provide the functionality of integration and sharing weather data. When compared to other discussed systems, \acrshort{dias} and \acrshort{madis} do not provide the workflow capabilities. The \acrshort{dias} converts data using a inbuilt set of \acrshort{api}s to store data on a large volume of disk space. It also provides some functionalities to quality control the data, and metadata management, and shares the data through a shared API layer. The \acrshort{madis} stores the data after converts into a common data format, and allow role based data access.
As mentioned above, most systems uses monolithic architecture or client service architecture, platform dependent, and not up to date with cloud computing technologies. Thus users can not benefit from modern cloud platforms and not able to decide the best cost-effective way to host the system. Since most systems are proprietary or closed source, it is difficult to add new requirements and maintain the system in long-term.

@@

As shown in Figure 3.4, when a request with a larger size comes to the system, it stores the data for asynchronously process the data and responds with a unique id that can use to verify whether data processed successfully or not. First it stores the data and publish an event to another service to process it. After successfully process the data by other service, it updates the system status. Also the \acrshort{wdias} provides a simple RESTful API to interact with timeseries metadata and other modules such as import, export and extension modules.
\dbc{Drop the REST API. No need for a paper. You can briefly mention it.}
\gkc{Removed}

@@

During the performance test, it creates 1000 timeseries using the locations are taken from Google's Countries Public Data set \cite{GoogleGoogleCounties}, and uses static 100 Grid locations for store Grid data. Load test perform using  JMeter and used the Distributed Testing feature to generate higher load. It uses the master-slave approach and it allowed to handle all the test cases via single instance, rather handling separate instances. The system is capable of storing any numeric value up to 3 decimal points. It does not make any difference based on the parameter type whether it is the precipitation or the temperature. Thus during the performance testing,  JMeter uses real precipitation data from \acrshort{curw}. One month period of data for five weather stations has been using to prepare the test data.

@@

\cref{ptab:obs_all_auto_15_min_summary_throughput} shows the \acrshort{wdias} performance with 15minutes data, but enabled auto-scaling. During above test cases, most resource utilized module was importing Grid data.
The observations are almost similar to \cref{ptab:obs_all_15_min_summary_throughput}, but notably the error rate of insert Grid timeseries got reduced after enabled the auto-scaling for import Grid data module. Also the standard deviation for handling Grid data reduced which means system was able to perform more better than the previous test plan.

@@

\emph{Risk of unable to process data} during the test performance, the \acrshort{wdias} processed many requests with higher request size than the normal usage with a lower rate of failures to process the requests, mainly with insert Grid data. If the usage of \acrshort{wdias} wants to reduce the risk of unable to process data, then the system can configure to run with redundant pods to handle spike of workloads. Also while configuring for the auto-scaling, the \acrshort{k8s} can configure to maintain a lower amount of CPU usage such as 50\% to 60\% rather  than 80\%. Such configuration with always spawn new pods to handle double of current peak load.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Discussion}
\label{psubse:discussion}
\dbc{Make this the discussion and a sub-section of Sec. 4}
\gkc{Renamed. I did not get what did you mean by sub section 4. Did you mean \cref{pse:summary}?}

>>>>

\begin{IEEEkeywords}
\db{Cloud computing, data assimilation, data integration, }microservice, weather
\end{IEEEkeywords}
\dbc{Update keyword list based on thesis. 4-5 keywords max}
\gkc{Thesis keywords are Cloud computing, data assimilation, data integration, hierarchical databases, microservice, weather. Do we need different set of keywords?}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
\label{pse:Introduction}
Weather prediction is essential to reduce the impacts caused by natural disasters and to effectively manage natural water resources. To enhance the accuracy of weather predictions, it requires to provide reliable and detailed weather data as inputs to \acrfull{nwm}s. Before feeding such diverse data collected from different sources, we need to convert data into NWMs compatible data format. Further we need to process data with lesser time to increase the lead time of forecasting, and need to handle bulk stream weather data.
Many third-party applications and researcher need to accessed processed weather data to make use of them. As few examples, logistics companies could use those data with their models to plan and schedule their deliveries. Agricultural insurance companies can warn the farmers, as well as calculate premiums based on anticipated weather patterns.
Even though there are many data integration systems, most systems are proprietary or closed source. For an island like Sri Lanka that having different kinds of weather seasons over the year than that software originated countries, those systems need to be highly customized. Thus, it required to get support from the vendor to integrate and configure the system.
Most of the software existing out there are not up to date with the latest technology concepts such as Cloud Computing, and not using modern architecture pattern like microservice architecture that can use to build highly scalable and available systems, and use containerized applications to run systems independ of software platforms.

\db{Several forecasting systems are} developed with considering above factors for disaster management. Deltares developed the The \acrfull{fews} \cite{Werner2013TheSystem} in the Netherland for operational forecasting. It uses a model-centric approach, and implements the forecasting process as a combination of data modeling steps and data transformation algorithms. This framework does not have inherent hydrological modeling capabilities. But it capable of providing capability to create forecast workflows by integrate new models and algorithms. Also, it uses a common data-model approach, and only allows models to interact with the system data via using one of the interfaces provided. All the timeseries data store in the common data model. This approach can consider as efficient for data store and access, but it has the inherent performance issues of access data in the database through a single data model. Interestingly, the \acrshort{fews} uses set of unique fields to identify timeseries one from another such as using timeseries's location and data type, as well as an id related to the source of the data. It provides an easy model integration with using the concept of the open modeling framework proposed by Open model integration \cite{Kokkonen2003InterfacingXML}. But the model adapter causes tide couple between models and the execution process of the \acrshort{fews}. This can cause issues when it required to do model unit testing and restrict the flexibility of running the models with parallel execution or external process execution.

\acrfull{lead} \cite{Droegemeier2005Service-OrientedWeather} uses the concept of dynamic workflow orchestration and data management in a Web services framework. To predict and analyze weather models by researchers, it requires many resources. Rather than each researcher runs and maintain own computer resources for the weather experiments, the \acrshort{lead} provides a pool of resources. The researchers use the resources pool to run their experiment in shorter amounts of time in higher scale. The \acrshort{lead} follows \acrfull{soa} with different service layers. Also, it exposes services through a drag and drop interface to create new workflows. A workflow service in the \acrshort{lead} schedules and run built workflows with promising the maximum use of underline resource pool. \acrfull{dias} \cite{Kawasaki2018DataReduction} and \acrfull{madis} \cite{Macdermaid2005ArchitectureP2.39} provide the functionality of integration and sharing weather data. When compared to other discussed systems, \acrshort{dias} and \acrshort{madis} do not provide the workflow capabilities. The \acrshort{dias} converts data using a inbuilt set of \acrshort{api}s to store data on a large volume of disk space. It also provides some functionalities to quality control the data, and metadata management, and shares the data through a shared API layer. The \acrshort{madis} stores the data after converts into a common data format, and allow role based data access.
As mentioned above, most systems uses monolithic architecture or client service architecture, platform dependent, and not up to date with cloud computing technologies. Thus, users cannot benefit from modern cloud platforms and not able to decide the best cost-effective way to host the system. Since most systems are proprietary or closed source, it is difficult to add new requirements and maintain the system in long-term.

@@

As shown in Figure 3.4, when a request with a larger size comes to the system, it stores the data for asynchronously process the data and responds with a unique id that can use to verify whether data processed successfully or not. First it stores the data and publish an event to another service to process it. After successfully process the data by other service, it updates the system status. Also, the \acrshort{wdias} provides a simple RESTful API to interact with timeseries metadata and other modules such as import, export and extension modules.
\dbc{Drop the REST API. No need for a paper. You can briefly mention it.}
\gkc{Removed}

@@

During the performance test, it creates 1000 timeseries using the locations are taken from Google's Countries Public Data set \cite{GoogleGoogleCounties}, and uses static 100 Grid locations for store Grid data. Load test perform using  JMeter and used the Distributed Testing feature to generate higher load. It uses the master-slave approach and it allowed to handle all the test cases via single instance, rather handling separate instances. The system is capable of storing any numeric value up to 3 decimal points. It does not make any difference based on the parameter type whether it is the precipitation or the temperature. Thus, during the performance testing,  JMeter uses real precipitation data from \acrshort{curw}. One month period of data for five weather stations has been using to prepare the test data.

@@

\cref{ptab:obs_all_auto_15_min_summary_throughput} shows the \acrshort{wdias} performance with 15minutes data, but enabled auto-scaling. During above test cases, most resource utilized module was importing Grid data.
The observations are almost similar to \cref{ptab:obs_all_15_min_summary_throughput}, but notably the error rate of insert Grid timeseries got reduced after enabled the auto-scaling for import Grid data module. Also, the standard deviation for handling Grid data reduced which means system was able to perform more better than the previous test plan.

@@

\emph{Risk of unable to process data} during the test performance, the \acrshort{wdias} processed many requests with higher request size than the normal usage with a lower rate of failures to process the requests, mainly with insert Grid data. If the usage of \acrshort{wdias} wants to reduce the risk of unable to process data, then the system can configure to run with redundant pods to handle spike of workloads. Also, while configuring for the auto-scaling, the \acrshort{k8s} can configure to maintain a lower amount of CPU usage such as 50\% to 60\% rather  than 80\%. Such configuration with always spawn new pods to handle double of current peak load.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Discussion}
\label{psubse:discussion}
\dbc{Make this the discussion and a sub-section of Sec. 4}
\gkc{Renamed. I did not get what did you mean by sub Section 4. Did you mean \cref{pse:summary}?}

### 2020-05-06 introduction/sec_1-motivation.tex
v5.0
v5.1
After Dilum sir fixes
Added fixes
Error Term,Correct Term,Description,No of Occurrences,Pages (absolute)
a.k.a.,aka.,,Shoudl be aka and need a comma,1,-1
[a-z] as well as,, as well as,Needs a comma before,3,-1
Also,Also,,Comma should be used at beginning of a sentence,1,-1
can not,cannot,Is a single word,4,-1
[fF]igure.\d,Figure n,There has to be a space like Figure 2.7,82,-1
Hence,Hence,,Comma should be used at beginning of a sentence,1,-1
in order to,to,Can be replaced with just to in many cases,4,-1
in to,into,Is a single word,1,-1
may be,maybe,Is a single word,2,-1
section,Sectio

Weather prediction is essential to reduce the impact caused by natural disasters and to effectively manage natural resources like water. 
%It will give more understanding of weather prediction if we look into a weather prediction workflow that can use to predict the surface water level. 
The weather predictions/forecasts are performed using \acrfull{nwm} that use a set of configuration parameters and the current status of the environment such as temperature, rainfall, and wind direction as the inputs. For example, the \acrfull{wrf} \cite{MesoscaleMicroscaleMeteorologyLaboratoryWeatherModel} model is used to predict the rainfall, temperature, and wind direction. Typically multiple \acrshort{nwm} are executed on the same data with different configuration parameters. Then using the real-time observations, the most fitting model is selected. After removing the bias, the data extracted from a \acrshort{nwm} are then fed into another set of models/simulators. For example, FLO2D, a hydrologic model that predicts surface water level, could use precipitation estimates from \acrshort{wrf} to forecast flood levels.
\gkc{Removed the sentence. I tried to use the FLO2D as a model which can use WRF output to forecast water levels.}
\dbc{I fixed the sentence. Check whether it was ok. It was a pathetic effort to remove the sentence than trying to fix it.}

\acrfull{curw} \cite{CUrWSL2017SL} is tasked with the mission to reduce water-related natural disasters in Sri Lanka. \acrshort{curw} \cite{CUrWSLObservedSL} is implementing own system with the idea of long-term maintainability rather than depending on existing weather data integration systems. \acrshort{curw} collects real-time data from weather stations and other relevant entities and generates daily forecasts. Then the generated results are shared with relevant public departments responsible for disaster planning, risks mitigation, and disaster management. One of the future goals of \acrshort{curw} is to open up data to the public enabling both societal and commercial use cases.

@@

Weather data processed by one \acrshort{nwm} may be used by several other NWSs, as well as by many third-party applications and researcher. For example, logistic companies could use the processed data with their models to plan and schedule their deliveries. Agricultural insurance companies can warn the farmers, as well as calculate premiums based on the anticipated weather patterns. Besides, farmers could rely on weather forecasts to plan their work. % decide what work to do on a given day. For example, drying hay is only possible in dry weather. Also, the aeronautical industry is particularly sensitive to weather conditions, precise weather forecasts are essential since before takeoff a flight need to check the conditions on expected route and at destination.
%required a provide platform to provide such 3rd party access, and use the data or process those based on their applications.

>>>>

Weather prediction is essential to reduce the impact caused by natural disasters and to effectively manage natural resources like water. 
%It will give more understanding of weather prediction if we look into a weather prediction workflow that can use to predict the surface water level. 
The weather predictions/forecasts are performed using \acrfull{nwm} that use a set of configuration parameters and the current status of the environment such as temperature, rainfall, and wind direction as the inputs. For example, the \acrfull{wrf} \cite{MesoscaleMicroscaleMeteorologyLaboratoryWeatherModel} model is used to predict the rainfall, temperature, and wind direction. Typically multiple \acrshort{nwm} are executed on the same data with different configuration parameters. Then using the real-time observations, the most fitting model is selected. After removing the bias, the data extracted from a \acrshort{nwm} are then fed into another set of models/simulators. For example, FLO2D, a hydrologic model that predicts surface water level, could use precipitation estimates from \acrshort{wrf} to forecast flood levels.

\acrfull{curw} \cite{CUrWSL2017SL} is tasked with the mission to reduce water-related natural disasters in Sri Lanka. \acrshort{curw} \cite{CUrWSLObservedSL} is implementing own system with the idea of long-term maintainability rather than depending on existing weather data integration systems. \acrshort{curw} collects real-time data from weather stations and other relevant entities and generates daily forecasts. Then the generated results are shared with relevant public departments responsible for disaster planning, risks mitigation, and disaster management. One of the future goals of \acrshort{curw} is to open up data to the public enabling both societal and commercial use cases.
\dbc{Tru to use ``weather forecast'' than ``weather prediction''}

@@

Weather data processed by one \acrshort{nwm} maybe used by several other NWSs, as well as by many third-party applications and researcher. For example, logistic companies could use the processed data with their models to plan and schedule their deliveries. Agricultural insurance companies can warn the farmers, as well as calculate premiums based on the anticipated weather patterns. Besides, farmers could rely on weather forecasts to plan their work. % decide what work to do on a given day. For example, drying hay is only possible in dry weather. Also, the aeronautical industry is particularly sensitive to weather conditions, precise weather forecasts are essential since before takeoff a flight need to check the conditions on expected route and at destination.
%required a provide platform to provide such 3rd party access, and use the data or process those based on their applications.

### 2020-05-06 lit/sec_1-fews.tex
v5.0
Added fixes
Error Term,Correct Term,Description,No of Occurrences,Pages (absolute)
a.k.a.,aka.,,Shoudl be aka and need a comma,1,-1
[a-z] as well as,, as well as,Needs a comma before,3,-1
Also,Also,,Comma should be used at beginning of a sentence,1,-1
can not,cannot,Is a single word,4,-1
[fF]igure.\d,Figure n,There has to be a space like Figure 2.7,82,-1
Hence,Hence,,Comma should be used at beginning of a sentence,1,-1
in order to,to,Can be replaced with just to in many cases,4,-1
in to,into,Is a single word,1,-1
may be,maybe,Is a single word,2,-1
section,Section,S should be capital if us

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{\acrshort{fews} flow forecasting system}
\label{se:fews}

@@

One of the simple and most useful features in the Delft-FEWS is the use of an open approach to integrate models and data. The concept of the open modeling framework is used by the Delft-FEWS, which is proposed by open model integration \cite{Kokkonen2003InterfacingXML}. It merely gives the flexibility to allow operators to integrate more models as well as variations of the same model and come up with new forecasting flows as much as possible.

The users need to configure the input timeseries data via XML configurations, and Delft-FEWS generates the model input data as XML files. As shown in \cref{fi:fews_general_adapter}, a model adapter transforms the data into the required format for the model as a preprocessing step. The Delft-FEWS has prebuilt a set of model adapters, and users can use available model adapters. Next, the Delft-FEWS executes the external model, which generates the model output, and allows users to run multiple models parallel or run those sequentially as needed. In the post-processing step, the results of the model transform into an XML file, which imports into the database through the data access layer, as shown in \cref{fi:fews_general_adapter} \cite{Werner2013TheSystem}. The general adapter used by the Delft-FEWS for the model execution is causing tide coupling into the execution process in the system. Users do not have the flexibility to run the models with different configurations, such as parallel execution of a particular model. Those issues may be overcome by triggering an external process at the execution time. But, it introduces more difficulty in handling the next step in the forecasting flow, after the successful execution of the model.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Delft-FEWS flow forecasting system}
\label{se:fews}

@@

One of the simple and most useful features in the Delft-FEWS is the use of an open approach to integrate models and data. The concept of the open modeling framework is used by the Delft-FEWS, which is proposed by open model integration \cite{Kokkonen2003InterfacingXML}. It merely gives the flexibility to allow operators to integrate more models, as well as variations of the same model and come up with new forecasting flows as much as possible.

The users need to configure the input timeseries data via XML configurations, and Delft-FEWS generates the model input data as XML files. As shown in \cref{fi:fews_general_adapter}, a model adapter transforms the data into the required format for the model as a preprocessing step. The Delft-FEWS has prebuilt a set of model adapters, and users can use available model adapters. Next, the Delft-FEWS executes the external model, which generates the model output, and allows users to run multiple models parallel or run those sequentially as needed. In the post-processing step, the results of the model transform into an XML file, which imports into the database through the data access layer, as shown in \cref{fi:fews_general_adapter} \cite{Werner2013TheSystem}. The general adapter used by the Delft-FEWS for the model execution is causing tide coupling into the execution process in the system. Users do not have the flexibility to run the models with different configurations, such as parallel execution of a particular model. Those issues maybe overcome by triggering an external process at the execution time. But, it introduces more difficulty in handling the next step in the forecasting flow, after the successful execution of the model.

### 2020-05-06 lit/sec_3-other-systems.tex
Added fixes
Error Term,Correct Term,Description,No of Occurrences,Pages (absolute)
a.k.a.,aka.,,Shoudl be aka and need a comma,1,-1
[a-z] as well as,, as well as,Needs a comma before,3,-1
Also,Also,,Comma should be used at beginning of a sentence,1,-1
can not,cannot,Is a single word,4,-1
[fF]igure.\d,Figure n,There has to be a space like Figure 2.7,82,-1
Hence,Hence,,Comma should be used at beginning of a sentence,1,-1
in order to,to,Can be replaced with just to in many cases,4,-1
in to,into,Is a single word,1,-1
may be,maybe,Is a single word,2,-1
section,Section,S should be capital if used li

Some of the MADIS data is considered to be the property of the supplier, and data access should be provided based on the authorization. In order to address the issue, MADIS data is divided into six different versions, depending on the access level authorized by the data provider \cite{Macdermaid2005ArchitectureP2.39}. When compared to Delft-FEWS, MADIS provides control-based access to the data.

>>>>

Some of the MADIS data is considered to be the property of the supplier, and data access should be provided based on the authorization. To address the issue, MADIS data is divided into six different versions, depending on the access level authorized by the data provider \cite{Macdermaid2005ArchitectureP2.39}. When compared to Delft-FEWS, MADIS provides control-based access to the data.

### 2020-05-06 method/sec_1-architectural_decisions.tex
Added fixes
Error Term,Correct Term,Description,No of Occurrences,Pages (absolute)
a.k.a.,aka.,,Shoudl be aka and need a comma,1,-1
[a-z] as well as,, as well as,Needs a comma before,3,-1
Also,Also,,Comma should be used at beginning of a sentence,1,-1
can not,cannot,Is a single word,4,-1
[fF]igure.\d,Figure n,There has to be a space like Figure 2.7,82,-1
Hence,Hence,,Comma should be used at beginning of a sentence,1,-1
in order to,to,Can be replaced with just to in many cases,4,-1
in to,into,Is a single word,1,-1
may be,maybe,Is a single word,2,-1
section,Section,S should be capital if used li

The \acrshort{esb} has the processing units called \emph{mediators}. A mediator can take a message, carry out some predefined actions on it, and output the modified message. These mediator capabilities can be used to integrate the modules of a weather data system, as shown in \cref{fi:wdia_components}. \acrshort{esb} also supports different transportation protocols such as HTTP and Web sockets. However, we realized that \acrshort{esb} is not suitable for data streaming or bulk data processing. Also, \acrshort{esb} suffers from a single point of failure, as all the messages are going through a common shared bus and slower communication (can not be used for transfer data). In the second design phase of \acrshort{wdias}, we attempted to use the actor model using the AKKA framework \cite{HewittWhyModel} to overcome above \acrshort{esb} drawbacks. At the same time, we moved away from the \acrshort{soa} architecture design to the microservice architecture design.

Thus we redesigned the system architecture with decomposing into microservices and used actors to implement each microservice in the system. In that case, we mapped each microservice in \acrshort{wdias} to an actor or an actor with slave actors. \acrshort{soa} focuses on imperative programming, while the microservices architecture focuses on a reactive actor programming style using faster messaging mechanisms.
When compared to \acrshort{soa}, the microservice architecture has several advantages:
\begin{itemize}
    \item Follow the principle of a single responsibility.
    \item Resilient/flexible because a failure of service does not influence other services. If you have monolithic or significant service errors in a service/module, this can have an impact on other modules/functionalities.
    \item High scalability because demanding services can be deployed on different servers to improve performance and stay away from other services so that they do not affect other services. It will be challenging to achieve the same with a single large monolithic service.
    \item Easy to improve the system because the microservices are decoupled from other services. It is also easier to change and test each microservices.
    \item Little impact on other services because each service is independent.
    \item Easy to understand because they represent a small functionality.
    \item Ease of deployment.
\end{itemize}

>>>>

The \acrshort{esb} has the processing units called \emph{mediators}. A mediator can take a message, carry out some predefined actions on it, and output the modified message. These mediator capabilities can be used to integrate the modules of a weather data system, as shown in \cref{fi:wdia_components}. \acrshort{esb} also supports different transportation protocols such as HTTP and Web sockets. However, we realized that \acrshort{esb} is not suitable for data streaming or bulk data processing. Also, \acrshort{esb} suffers from a single point of failure, as all the messages are going through a common shared bus and slower communication (cannot be used for transfer data). In the second design phase of \acrshort{wdias}, we attempted to use the actor model using the AKKA framework \cite{HewittWhyModel} to overcome above \acrshort{esb} drawbacks. At the same time, we moved away from the \acrshort{soa} architecture design to the microservice architecture design.

Thus, we redesigned the system architecture with decomposing into microservices and used actors to implement each microservice in the system. In that case, we mapped each microservice in \acrshort{wdias} to an actor or an actor with slave actors. \acrshort{soa} focuses on imperative programming, while the microservices architecture focuses on a reactive actor programming style using faster messaging mechanisms.
When compared to \acrshort{soa}, the microservice architecture has several advantages:
\begin{itemize}
    \item Follow the principle of a single responsibility.
    \item Resilient/flexible because a failure of service does not influence other services. If you have monolithic or significant service errors in a service/module, this can have an impact on other modules/functionalities.
    \item High scalability because demanding services can be deployed on different servers to improve performance and stay away from other services so that they do not affect other services. It will be challenging to achieve the same with a single large monolithic service.
    \item Easy to improve the system because the microservices are decoupled from other services. It is also easier to change and test each microservices.
    \item Little impact on other services because each service is independent.
    \item Easy to understand because they represent a small functionality.
    \item Ease of deployment.
\end{itemize}

### 2020-05-06 method/sec_3-microservice.tex
Added fixes
Error Term,Correct Term,Description,No of Occurrences,Pages (absolute)
a.k.a.,aka.,,Shoudl be aka and need a comma,1,-1
[a-z] as well as,, as well as,Needs a comma before,3,-1
Also,Also,,Comma should be used at beginning of a sentence,1,-1
can not,cannot,Is a single word,4,-1
[fF]igure.\d,Figure n,There has to be a space like Figure 2.7,82,-1
Hence,Hence,,Comma should be used at beginning of a sentence,1,-1
in order to,to,Can be replaced with just to in many cases,4,-1
in to,into,Is a single word,1,-1
may be,maybe,Is a single word,2,-1
section,Section,S should be capital if used li

\paragraph{Z-axis Scaling}-- The Z-axis scaling follows the concept of each service running the same application code (similar to X-axis scaling). The big difference is that each service is responsible for only a subset of the data. Z-axis splits are commonly used to scale databases. As an example, data partition (a.k.a. sharded) across a set of servers based on an attribute of each record.
Even our research is a design based on the Y-axis scaling; it is possible to use the Z-axis scaling to further scaling the system. We will discuss more detail in \cref{se:discussion}.

@@

\cref{fi:wdias_micro_on_demand} and \cref{fi:wdias_micro_async} show the system interaction of the WDIA microservices architecture while handling the requests. Each circle in the Figures represents a microservice in the \acrshort{wdias}. And each microservice is implemented as a containerized application. The left side of \cref{fi:wdias_micro_on_demand} shows the import modules of the \acrshort{wdias}, and the right side shows the export modules. Also, we implemented each module as a microservice to independent maintainability and upgradability. We followed the concept of smart endpoints and dumb pipes explained in \cref{subse:dumb_pipes}, and each import microservice only does the specific task of converting and forwarding the request to the correct data adapter module. For scalar, vector, and grid data types, we created adapter microservices that are optimized for storing such kinds of data. And the metadata data of the timeseries store using an RDBMS, which gives more performance over retrieving timeseries metadata. The metadata is cached using an In-Memory database to fast access while implementing the database structure. The system generates a unique identifier for each timeseries, and throughout the \acrshort{wdias} system, all microservices use it to handle data for fast access.

@@

Other than the above endpoints, we exposed another set of endpoints to configure extensions, and we will describe further in \cref{se:data_preprocess}.
Other than the timeseries metadata endpoints, other module endpoints start with the module name such as import, export, and extension when compared to timeseries metadata endpoints. Using the above convention, we allowed adding a new module system if required.
For import and export modules, the names of the endpoints defined as the modules name then follow the data format. The above endpoint naming convention provides the flexibility to integrate new data format modules for import and export. Then the endpoint name ends with the type of data operation. Data can upload as a single file with binary or multiple files with the upload. Other than that, users can send requests with raw data with required headers has mentioned by a particular import module.
Thus the \acrshort{api} convention of \texttt{/MODULE/DATA\_FORMAT/DATA\_TYPE} allows users to integrate new import or export modules into the system as well as add new data types.

>>>>

\paragraph{Z-axis Scaling}-- The Z-axis scaling follows the concept of each service running the same application code (similar to X-axis scaling). The big difference is that each service is responsible for only a subset of the data. Z-axis splits are commonly used to scale databases. As an example, data partition (aka., sharded) across a set of servers based on an attribute of each record.
Even our research is a design based on the Y-axis scaling; it is possible to use the Z-axis scaling to further scaling the system. We will discuss more detail in \cref{se:discussion}.

@@

\cref{fi:wdias_micro_on_demand} and \cref{fi:wdias_micro_async} show the system interaction of the WDIA microservices architecture while handling the requests. Each circle in the figures represents a microservice in the \acrshort{wdias}. And each microservice is implemented as a containerized application. The left side of \cref{fi:wdias_micro_on_demand} shows the import modules of the \acrshort{wdias}, and the right side shows the export modules. Also, we implemented each module as a microservice to independent maintainability and upgradability. We followed the concept of smart endpoints and dumb pipes explained in \cref{subse:dumb_pipes}, and each import microservice only does the specific task of converting and forwarding the request to the correct data adapter module. For scalar, vector, and grid data types, we created adapter microservices that are optimized for storing such kinds of data. And the metadata data of the timeseries store using an RDBMS, which gives more performance over retrieving timeseries metadata. The metadata is cached using an In-Memory database to fast access while implementing the database structure. The system generates a unique identifier for each timeseries, and throughout the \acrshort{wdias} system, all microservices use it to handle data for fast access.

@@

Other than the above endpoints, we exposed another set of endpoints to configure extensions, and we will describe further in \cref{se:data_preprocess}.
Other than the timeseries metadata endpoints, other module endpoints start with the module name such as import, export, and extension when compared to timeseries metadata endpoints. Using the above convention, we allowed adding a new module system if required.
For import and export modules, the names of the endpoints defined as the modules name then follow the data format. The above endpoint naming convention provides the flexibility to integrate new data format modules for import and export. Then the endpoint name ends with the type of data operation. Data can upload as a single file with binary or multiple files with the upload. Other than that, users can send requests with raw data with required headers has mentioned by a particular import module.
Thus, the \acrshort{api} convention of \texttt{/MODULE/DATA\_FORMAT/DATA\_TYPE} allows users to integrate new import or export modules into the system, as well as add new data types.
